Implicit yaddayadda

### 2011-10-28 papers/PLDI2012/implicitization.tex
Gulwani c'est disjunctive

Assuming we are  interested in a loop-free program fragment, the above approach of keeping symbolic unions gives the same results as performing the analysis separately over every path in the fragment.
A recent method for finding inductive loop invariants \cite{DBLP:conf/pldi/GulwaniZ10} is based on this idea: each path inside the loop body is considered separately.
Two recent proposals use SMT-solving \cite{Kroening_Strichman_08} as a decision procedure for the satisfiability of first-order arithmetic formulas in order to enumerate only paths that are needed for the progress of the analysis \cite{Gawlitza_Monniaux_ESOP11,Monniaux_Gonnord_SAS11}. They can equivalently be seen as analyses over a multigraph of transitions between some distinguished control nodes. This multigraph has an exponential number of edges, but is never explicitly represented in memory; instead, this graph is \emph{implicitly} or \emph{succinctly} represented: its edges are enumerated as needed as solutions to SMT problems.

>>>>

Assuming we are  interested in a loop-free program fragment, the above approach of keeping symbolic unions gives the same results as performing the analysis separately over every path in the fragment.
A recent method for finding disjunctive loop invariants \cite{DBLP:conf/pldi/GulwaniZ10} is based on this idea: each path inside the loop body is considered separately.
Two recent proposals use SMT-solving \cite{Kroening_Strichman_08} as a decision procedure for the satisfiability of first-order arithmetic formulas in order to enumerate only paths that are needed for the progress of the analysis \cite{Gawlitza_Monniaux_ESOP11,Monniaux_Gonnord_SAS11}. They can equivalently be seen as analyses over a multigraph of transitions between some distinguished control nodes. This multigraph has an exponential number of edges, but is never explicitly represented in memory; instead, this graph is \emph{implicitly} or \emph{succinctly} represented: its edges are enumerated as needed as solutions to SMT problems.
